Boosted Regression Trees for Data-Driven Auto-Tuning

### 2011-12-09 paper/draft1.tex
m

\title{Boosted Regression Trees for Data-Driven Auto-Tuning}

@@

@@

The strategy we use for computing filterbank correlation on the GPU
using CUDA follows \citet{pinto+cox:2011gcg}.
The overall strategy is to load the filterbank into some relatively fast
memory (constant or texture), and then launch a grid of blocks that each
computes some local piece of the output image $z$.
Each thread computes $4 \times n\_output\_4s$ channels for some column and row of $z$.
Each block computes a subrectangle of the output $z$,
and the grid is used to tile the whole output image with blocks.
Some filterbanks are too large to fit into the fast memory.
For large filterbanks our approach permits splitting the filterbanks along
the number-of-filters dimension ($F$) and the number-of-rows dimension ($H$).
All the filterbanks in our study are small enough that at least half of each
filter can always fit into the constant or texture memory.
When splitting the filterbank in this way we must use several kernel
executions, each of which increments the output buffer by a partial result.
Pseudo-code for the kernel is given in Figure~\ref{fig:kernel}.

@@

\begin{align*}
\mathrm{block\_w}    & \in (4, 8, 16, 32, 64, 128) \\
\mathrm{block\_h}    & \in (4, 8, 16, 32, 64, 128) \\
\mathrm{n\_filter\_r} & \in (1, 2) \\
\mathrm{n\_output\_4s} & \in (\mathrm{all}, 1, 2) \\
\mathrm{spill}      & \in (False, True) \\
\mathrm{imul\_fast}  & \in (False, True) \\
\mathrm{pad\_shared} & \in (False, True) \\
\mathrm{use\_tex1d}  & \in (False, True) \\
\mathrm{maxrreg}    & \in (8, 16, 20, 24, 28, 32, \infty) \\
\mathrm{fast\_math}  & \in (False, True)
\end{align*}

@@

>>>>

%XXX:  Machine Learning for Auto-tuning: A Data-Drive Approach...} ???
\title{Boosted Regression Trees for Data-Driven Auto-Tuning}

@@

%XXX: DIAGRAM OF IMAGE, FILTERBANK, OUTPUT

@@

The strategy we use for computing filterbank correlation on the GPU
using CUDA follows \citet{pinto+cox:2011gcg}.
The overall strategy is to load the filterbank into constant memory, which is
relatively fast and visible to all threads, and then launch a grid of blocks
that tiles the output image.
Each thread computes $4 \times n\_output\_4s$ channels for some column and row of $z$.
Each block computes $4 \times n\_output\_4s$ channels for a subrectangle of the output image ($z$).
When there are more than $4 \times n\_output\_4s$ channels in $z$, or if the
filterbank is too large to fit into constant memory, then multiple
kernel executions perform the full computation.
Our approach permits splitting the filterbank along
the number-of-filters dimension ($F$) and the height dimension ($H$).
All the filterbanks in our study are small enough that
at least one row of a single filter can fit into constant memory.
Pseudo-code for the kernel is given in Figure~\ref{fig:kernel}.

@@

The kernel is parametrized by 10 parameters:
\begin{align*}
\mathrm{block\_h}    & \in (4, 8, 16, 32, 64, 128) \\
\mathrm{block\_w}    & \in (4, 8, 16, 32, 64, 128) \\
\mathrm{n\_filter\_r} & \in (1, 2) \\
\mathrm{n\_output\_4s} & \in (\mathrm{all}, 1, 2) \\
\mathrm{spill}      & \in (False, True) \\
\mathrm{imul\_fast}  & \in (False, True) \\
\mathrm{pad\_shared} & \in (False, True) \\
\mathrm{use\_tex1d}  & \in (False, True) \\
\mathrm{maxrreg}    & \in (8, 16, 20, 24, 28, 32, \infty) \\
\mathrm{fast\_math}  & \in (False, True)
\end{align*}

The block height (block\_h) and block width (block\_w) parameters control the
number of threads that run on each multiprocessor.
The number of filter rows (n\_filter\_r) is how many rows of each filter is
loaded

@@

XXXX: Talk about memory transfer requirements vs. speed vs. copy...
